Place of death in NRS COVID-19 deaths

### 2021-08-24 covid_nrs_place_of_death_visualisations.Rmd
fixed graph size so the subtitle doesn't get cut off!

save_output_file(filename = paste0(dir_outputs,"/figure_proportion_home_deaths_over_time"), extensions = c(".pdf",".svg",".png"), plot = figure_proportion_home_deaths_over_time, width = 12, height = 10, units = "cm", dpi = 300)
```

>>>>

save_output_file(filename = paste0(dir_outputs,"/figure_proportion_home_deaths_over_time"), extensions = c(".pdf",".svg",".png"), plot = figure_proportion_home_deaths_over_time, width = 13, height = 10, units = "cm", dpi = 300)
```
